---
title: "Primary Care Timeline Tool"
author: "NHS Transformation Unit"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: false
runtime: shiny
---

<style>
/* Cerulean Theme CSS */

/* Global Styles */
body {
    background-color: #fff; /* White background */
    color: #333; /* Dark text color */
    font-family: Franklin Gothic;
    font-size: 11pt;
    font-weight: 300;
}

h1, h2, h3, h4 {
  color: #407EC9;
}

hr {
  color: #407EC9;
  border-color: #407EC9;
}

/* Navbar Styles */
.navbar {
    background-color: #407EC9; /* Cerulean blue background */
    border-color: #407EC9; /* Cerulean blue border */
    color: #fff; /* White text color */
}

/* Button Styles */
.btn-primary {
    background-color: #407EC9; /* Cerulean blue button background */
    border-color: #407EC9; /* Cerulean blue button border */
    color: #fff; /* White text color */
}

/* Custom button style for pale blue */
.btn-download {
    background-color: #B2D6E0; /* Pale blue background */
    border-color: #B2D6E0; /* Pale blue border */
    color: #fff; /* White text color */
}

/* Links Styles */
a {
    color: #407EC9; /* Cerulean blue link color */
}

/* Add more styles as needed */

.toc.float-toc {
    margin-bottom: 20px; /* Adjust the margin as needed */
}
</style>

```{css, echo=FALSE}
    body .main-container {
      max-width: 1900px !important;
      width: 1900px !important;
    }
    body {
      max-width: 1900px !important;
    }
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(ggplot2)
library(dplyr)
library(readxl)
library(plotly)
library(kableExtra)
library(shiny)
library(fastmap)
library(lubridate)

source("../config/r_scripts/packages.R")
source("../data_processing/r_scripts/Data_Extraction_Processing.R")

# Loading the processed data
Pt_Proc_Wide <- read_excel("C:/Users/ejroy/OneDrive - Midlands and Lancashire CSU/Git/Primary-Care-Theograph/data/processed_extracts/Proc_Patient_Extract.xlsx")

Pt_Proc_Wide <- Pt_Proc_Wide %>%
  mutate(Contact_Event_Date = dmy(Contact_Event_Date, quiet = TRUE)) %>%
  filter(!is.na(Contact_Event_Date))

patient_names <- unique(Pt_Proc_Wide$Patient_Name)
```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/DIA_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")
```

## User guidance
***

Introductory text to be agreed with client, but will speak to purpose of tool, including its aims and limitations, as well as some guidance on how the tool is designed to be used.

## Categories explored within this tool
***

The time series below visualises patient X's GP contact history, displaying the following information:

* Date of contact.
* Any diagnoses made on date of contact.
* Any prescriptions (or changes to existing prescriptions) made on date of contact.
* The results of any relevant biomedical assays completed on date of contact.

```{r examplePlot, echo=FALSE}

library(dplyr)
library(ggplot2)
library(plotly)
library(shiny)

# Function to create time series plots
create_time_series_plot <- function(data, date_col, y_col, test_col, unit_col, vis_colour) {
  tryCatch({
    if (!(date_col %in% names(data)) | !(y_col %in% names(data)) | !(test_col %in% names(data)) | !(unit_col %in% names(data))) {
      stop("One or more specified columns are not found in the data frame.")
    }

    data <- data[!is.na(data[[y_col]]), ]

    data$tooltip_text <- paste0(
      "Date: ", format(data[[date_col]], "%d/%m/%Y"), "\n",  
      data[[test_col]], ": ", data[[y_col]], " ", data[[unit_col]]
    )

    y_label <- paste(data[[test_col]][1], "\n(", data[[unit_col]][1], ")", sep = "")

    plot <- ggplot(data, aes(x = !!sym(date_col), y = !!sym(y_col))) +
      geom_line(color = vis_colour) +
      geom_point(color = vis_colour, size = 2) +  
      labs(title = paste(data[[test_col]][1], "Over Time"),
           x = "Date",
           y = y_label) +
      scale_x_date(date_labels = "%d/%m/%Y") +
      theme_minimal() +
      theme(axis.title.y = element_text(size = 12))

    plotly_plot <- ggplotly(plot, tooltip = c("x", "y", "tooltip_text"))

    return(plotly_plot)
  }, error = function(e) {
    showNotification(paste("Error creating plot:", e$message), type = "error")
    NULL  
  })
}

# Shiny UI
ui <- fluidPage(
  tags$style(HTML("
    /* Cerulean Theme CSS */

    /* Global Styles */
    body {
    background-color: #fff; /* White background */
    color: #333; /* Dark text color */
    font-family: Franklin Gothic;
    font-size: 11pt;
    font-weight: 300;
}

h1, h2, h3, h4 {
  color: #407EC9;
}

hr {
  color: #407EC9;
  border-color: #407EC9;
}

/* Navbar Styles */
.navbar {
    background-color: #407EC9; /* Cerulean blue background */
    border-color: #407EC9; /* Cerulean blue border */
    color: #fff; /* White text color */
}

/* Button Styles */
.btn-primary {
    background-color: #407EC9; /* Cerulean blue button background */
    border-color: #407EC9; /* Cerulean blue button border */
    color: #fff; /* White text color */
}

/* Custom button style for pale blue */
.btn-download {
    background-color: #407EC9; /* Pale blue background */
    border-color: #407EC9; /* Pale blue border */
    color: #fff; /* White text color */
}

/* Links Styles */
a {
    color: #407EC9; /* Cerulean blue link color */
}

/* Add more styles as needed */

.toc.float-toc {
    margin-bottom: 20px; /* Adjust the margin as needed */
}
  ")),
  
  titlePanel("Primary Care Timeline Tool"),
  hr(),
  fluidRow(
    column(
      width = 4,
      h3("Patient selection"),
      hr(),
      p("This section allows you to search for a patient using either ID# or surname."),
      selectInput("patient_names", "Select Patient ID:", choices = patient_names)  
    ),
     column(
      width = 4,
      h3("Patient information"),
      hr(),
      uiOutput("patient_report")
     ),
    column(
    width = 4,
    h3("Contact summary"),
    hr(),
    p("Please use the button below to download the patient's entire GP event history as an Excel workbook file."),
    downloadButton("downloadData", label = "Download patient data", class = "btn-download")  
)
  ),
  
  fluidRow(
    column(
      width = 12,
      h3("GP Contact, Diagnosis and Prescription Timeline"),
      hr(),
      p("The time series below visualises patient X's GP contact history, displaying diagnoses, prescriptions, and assay results."),
      plotlyOutput("combined_plot")
    )
  )
)


# Server logic
server <- function(input, output) {
  
  ## Reactive expression to filter data by selected patient
  Pt_Wide_reactive <- reactive({
    req(input$patient_names)
    Pt_Proc_Wide %>%
      filter(Patient_Name == input$patient_names)
  })
  
  ## Generating time series plot based on selected patient
  output$combined_plot <- renderPlotly({
    filtered_data <- Pt_Wide_reactive()
    
    if (nrow(filtered_data) == 0) {
      return(NULL)
    }
    
    ## Function to create dynamic Y-axis labels for biomedical tests or drugs
    create_dynamic_label <- function(test_col, unit_col, drug_col, drug_unit_col, data) {
      first_non_na_test <- data[[test_col]][!is.na(data[[test_col]])][1]
      first_non_na_unit <- data[[unit_col]][!is.na(data[[unit_col]])][1]
      
      first_non_na_drug <- data[[drug_col]][!is.na(data[[drug_col]])][1]
      first_non_na_drug_unit <- data[[drug_unit_col]][!is.na(data[[drug_unit_col]])][1]
      
      if (!is.na(first_non_na_test)) {
        return(paste(first_non_na_test, "<br>", first_non_na_unit))
      } else if (!is.na(first_non_na_drug)) {
        return(paste(first_non_na_drug, "<br>", first_non_na_drug_unit))
      } else {
        return("Unknown Value")
      }
    }
    
    ## Generating individual plots
    plot_1 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Biomedical_Value_1", "Biomedical_Test_1", "Biomedical_1_Units", "blue")
    plot_2 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Drug_1_Value", "Drug_Name_1", "Drug_1_Units", "lightblue")
    plot_3 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Biomedical_Value_2", "Biomedical_Test_2", "Biomedical_2_Units", "orange")
    plot_4 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Drug_2_Value", "Drug_Name_2", "Drug_2_Units", "yellow")
    
    ## Creating dynamic Y-axis labels with line breaks
    y_label_1 <- create_dynamic_label("Biomedical_Test_1", "Biomedical_1_Units", "Drug_Name_1", "Drug_1_Units", filtered_data)
    y_label_2 <- create_dynamic_label("Biomedical_Test_2", "Biomedical_2_Units", "Drug_Name_2", "Drug_2_Units", filtered_data)
    y_label_3 <- create_dynamic_label("Biomedical_Test_1", "Biomedical_1_Units", "Drug_Name_1", "Drug_1_Units", filtered_data)
    y_label_4 <- create_dynamic_label("Biomedical_Test_2", "Biomedical_2_Units", "Drug_Name_2", "Drug_2_Units", filtered_data)
    
    ## Creating a combined subplot without Y-axis titles and use annotations instead
    combined_plot <- subplot(list(plot_1, plot_2, plot_3, plot_4), 
                             nrows = 4, 
                             shareX = TRUE, 
                             titleX = TRUE) %>%
                     layout(
                       xaxis = list(rangeslider = list(visible = FALSE), fixedrange = TRUE),
                       yaxis = list(showticklabels = TRUE, automargin = TRUE),
                       yaxis2 = list(showticklabels = TRUE, automargin = TRUE),
                       yaxis3 = list(showticklabels = TRUE, automargin = TRUE),
                       yaxis4 = list(showticklabels = TRUE, automargin = TRUE),
                       
                       ## Adding annotations to replace Y-axis titles with horizontal text
                       annotations = list(
                         list(x = -0.07, y = 0.85, text = y_label_1, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12)),
                         list(x = -0.07, y = 0.63, text = y_label_2, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12)),
                         list(x = -0.07, y = 0.41, text = y_label_3, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12)),
                         list(x = -0.07, y = 0.19, text = y_label_4, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12))
                       )
                     )
    
    combined_plot
  })
  
  ## Generating patient report based on selected patient
  output$patient_report <- renderUI({
  filtered_data <- Pt_Wide_reactive()
  
  if (nrow(filtered_data) == 0) {
    return("No data available for the selected patient.")
  }
  
  patient_name <- trimws(filtered_data$Patient_Name[1])
  patient_gender <- trimws(filtered_data$Patient_Gender[1])
  
  diagnoses <- filtered_data %>%
    select(First_Diagnosis, Second_Diagnosis, Contact_Event_Date) %>%
    filter(!is.na(First_Diagnosis) | !is.na(Second_Diagnosis))
  
  ## Diagnosis logic
  diagnosis_report <- "No formal diagnoses to date."
  if (nrow(diagnoses) > 0) {
    diagnosis_entries <- character()
    
    if (!is.na(diagnoses$First_Diagnosis[1])) {
      first_diagnosis <- trimws(diagnoses$First_Diagnosis[1])
      first_diagnosis_date <- diagnoses$Contact_Event_Date[which(!is.na(diagnoses$First_Diagnosis))[1]]
      diagnosis_entries <- c(diagnosis_entries, paste(first_diagnosis, "on", format(first_diagnosis_date, "%d/%m/%Y")))
    }
    
    if (!is.na(diagnoses$Second_Diagnosis[1])) {
      second_diagnosis <- trimws(diagnoses$Second_Diagnosis[1])
      second_diagnosis_date <- diagnoses$Contact_Event_Date[which(!is.na(diagnoses$Second_Diagnosis))[1]]
      diagnosis_entries <- c(diagnosis_entries, paste(second_diagnosis, "on", format(second_diagnosis_date, "%d/%m/%Y")))
    }
    
    if (length(diagnosis_entries) > 0) {
      diagnosis_report <- paste("Patient diagnosed with", 
                                 paste(diagnosis_entries, collapse = " and "), 
                                 sep = " ")
    }
  }
  
  ## Prescription logic
  prescriptions <- filtered_data %>%
    select(First_Drug_Name, Second_Drug_Name, Contact_Event_Date) %>%
    filter(!is.na(First_Drug_Name) | !is.na(Second_Drug_Name))

  prescription_report <- "No prescriptions to date."
  if (nrow(prescriptions) > 0) {
    prescription_entries <- character()
    
    if (!is.na(prescriptions$First_Drug_Name[1])) {
      first_drug <- trimws(prescriptions$First_Drug_Name[1])
      first_drug_date <- prescriptions$Contact_Event_Date[which(!is.na(prescriptions$First_Drug_Name))[1]]
      prescription_entries <- c(prescription_entries, paste(first_drug, "on", format(first_drug_date, "%d/%m/%Y")))
    }
    
    if (!is.na(prescriptions$Second_Drug_Name[1])) {
      second_drug <- trimws(prescriptions$Second_Drug_Name[1])
      second_drug_date <- prescriptions$Contact_Event_Date[which(!is.na(prescriptions$Second_Drug_Name))[1]]
      prescription_entries <- c(prescription_entries, paste(second_drug, "on", format(second_drug_date, "%d/%m/%Y")))
    }
    
    if (length(prescription_entries) > 0) {
      prescription_report <- paste("Patient prescribed", 
                                   paste(prescription_entries, collapse = " and "), 
                                   sep = " ")
    }
  }
  
  if (!grepl("\\.$", diagnosis_report)) {
    diagnosis_report <- paste0(diagnosis_report, ".")
  }

  if (!grepl("\\.$", prescription_report)) {
    prescription_report <- paste0(prescription_report, ".")
  }

  ## Creating the final report
  report <- HTML(paste("<strong>Patient Name:</strong>", patient_name, "<br>",
                       "<strong>Sex:</strong>", patient_gender, "<br>",
                       "<strong>Diagnosis:</strong>", diagnosis_report, "<br>",
                       "<strong>Prescription(s):</strong>", prescription_report))
  report <- trimws(report)
  return(report)
})
  
  output$downloadData <- downloadHandler(
    filename = function() {
      paste("Theograph_Patient_Summary_", Sys.Date(), ".xlsx", sep = "")
    },
    content = function(file) {
      filtered_data <- Pt_Wide_reactive()
      write.xlsx(filtered_data, file)  
    }
  )
  
}

# Run the app
shinyApp(ui = ui, server = server)
```