---
title: "Primary Care Timeline Tool"
author: "NHS Transformation Unit"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: false
runtime: shiny
---

<style>
/* Cerulean Theme CSS */

/* Global Styles */
body {
    background-color: #fff; /* White background */
    color: #333; /* Dark text color */
    font-family: Franklin Gothic;
    font-size: 11pt;
    font-weight: 300;
}

h1, h2, h3, h4 {
  color: #407EC9;
}

hr {
  color: #407EC9;
  border-color: #407EC9;
}

/* Navbar Styles */
.navbar {
    background-color: #407EC9; /* Cerulean blue background */
    border-color: #407EC9; /* Cerulean blue border */
    color: #fff; /* White text color */
}

/* Button Styles */
.btn-primary {
    background-color: #407EC9; /* Cerulean blue button background */
    border-color: #407EC9; /* Cerulean blue button border */
    color: #fff; /* White text color */
}

/* Custom button style for pale blue */
.btn-download {
    background-color: #B2D6E0; /* Pale blue background */
    border-color: #B2D6E0; /* Pale blue border */
    color: #fff; /* White text color */
}

/* Links Styles */
a {
    color: #407EC9; /* Cerulean blue link color */
}

/* Add more styles as needed */

.toc.float-toc {
    margin-bottom: 20px; /* Adjust the margin as needed */
}

plot-container {
    max-width: 900px; /* Control the maximum width of the plot */
    margin-left: auto; /* Align to the right */
    margin-right: 0;
  }
</style>

```{css, echo=FALSE}
    body .main-container {
      max-width: 1700px !important;
      width: 1700px !important;
    }
    body {
      max-width: 1700px !important;
    }
    
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(ggplot2)
library(dplyr)
library(readxl)
library(plotly)
library(kableExtra)
library(shiny)
library(fastmap)
library(lubridate)

source("../config/r_scripts/packages.R")
source("../data_processing/r_scripts/Data_Extraction_Processing.R")

# Loading the processed data
Pt_Proc_Wide <- read_excel("C:/Users/elliot.royle/OneDrive - Midlands and Lancashire CSU/Git/Primary-Care-Theograph/data/processed_extracts/Proc_Patient_Extract.xlsx")

patient_names <- unique(Pt_Proc_Wide$Patient_Name)
```

```{r logo, echo = FALSE}

htmltools::img(src = knitr::image_uri(paste0(here(), "/images/DIA_logo_large.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:5%; padding:10px;',
               width = "180px",
               heigth = "180px")
```

## User guidance
***

Introductory text to be agreed with client, but will speak to purpose of tool, including its aims and limitations, as well as some guidance on how the tool is designed to be used.

## Categories explored within this tool
***

The time series below visualises patient X's GP contact history, displaying the following information:

* Date of contact.
* Any diagnoses made on date of contact.
* Any prescriptions (or changes to existing prescriptions) made on date of contact.
* The results of any relevant biomedical assays completed on date of contact.

```{r examplePlot, fig.height=18, echo=FALSE}

library(dplyr)
library(ggplot2)
library(plotly)
library(shiny)

# Function to create time series plots
create_time_series_plot <- function(data, date_col, y_col, test_col, unit_col, vis_colour) {
  tryCatch({
    if (!(date_col %in% names(data)) | !(y_col %in% names(data)) | !(test_col %in% names(data)) | !(unit_col %in% names(data))) {
      stop("One or more specified columns are not found in the data frame.")
    }

    # Check if the y_col and date_col have valid data
    if (all(is.na(data[[y_col]])) || nrow(data) == 0) {
      stop("The y_col has no valid data.")
    }

    data <- data[!is.na(data[[y_col]]), ]

    if (nrow(data) == 0) {
      stop("Filtered data has no rows after removing NA values.")
    }

    data$tooltip_text <- paste0(
      "Date: ", format(data[[date_col]], "%d/%m/%Y"), "\n",  
      data[[test_col]], ": ", data[[y_col]], " ", data[[unit_col]]
    )

    y_label <- paste(data[[test_col]][1], "\n(", data[[unit_col]][1], ")", sep = "")

    plot <- ggplot(data, aes(x = !!sym(date_col), y = !!sym(y_col))) +
      geom_line(color = vis_colour) +
      geom_point(color = vis_colour, size = 2) +  
      labs(title = paste(data[[test_col]][1], "Over Time"),
           x = "Date",
           y = y_label) +
      scale_x_date(date_labels = "%d/%m/%Y") +
      theme_minimal() +
      theme(axis.title.y = element_text(size = 12))

    plotly_plot <- ggplotly(plot, tooltip = c("x", "y", "tooltip_text")) %>%
      layout(margin = list(l = 250))  # Adjust the left margin as needed

    return(plotly_plot)
  }, error = function(e) {
    showNotification(paste("Error creating plot:", e$message), type = "error")
    return(NULL)  # Ensure a NULL return on error
  })
}

ui <- fluidPage(
  tags$head(
    tags$style(HTML("
      body {
        width: 100%;
        height: 100%;
        background-color: #fff; /* White background */
        color: #333; /* Dark text color */
        font-family: Franklin Gothic;
        font-size: 11pt;
        font-weight: 300;
      }

      /* Heading Styles */
      h1, h2, h3, h4 {
        color: #407EC9;
      }

      hr {
        color: #407EC9;
        border-color: #407EC9;
      }

      /* Navbar Styles */
      .navbar {
        background-color: #407EC9; /* Cerulean blue background */
        border-color: #407EC9; /* Cerulean blue border */
        color: #fff; /* White text color */
      }

      /* Button Styles */
      .btn-primary {
        background-color: #407EC9; /* Cerulean blue button background */
        border-color: #407EC9; /* Cerulean blue button border */
        color: #fff; /* White text color */
      }

      /* Custom download button style */
      .btn-download {
        background-color: #407EC9; /* Pale blue background */
        border-color: #407EC9; /* Pale blue border */
        color: #fff; /* White text color */
      }

      /* Link Styles */
      a {
        color: #407EC9; /* Cerulean blue link color */
      }

      /* Adjust TOC style */
      .toc.float-toc {
        margin-bottom: 20px;
      }
      
      .plot-container {
    max-width: 1400px; /* Control the maximum width of the plot */
    margin-left: auto; /* Align the plot to the right */
    margin-right: 0;
  }
    "))
  ),
  
  titlePanel("Primary Care Timeline Tool"),
  hr(),
  
  fluidRow(
  column(
      width = 4,
      h3("Patient selection"),
      hr(),
      p("This section allows you to search for a patient using either ID# or surname."),
      selectInput("patient_names", "Select Patient ID:", choices = patient_names)  
    ),
  column(
      width = 4,
      h3("Patient information"),
      hr(),
      uiOutput("patient_report")
    ),
  column(
      width = 4,
      h3("Contact summary"),
      hr(),
      p("Please use the button below to download the patient's entire GP event history as an Excel workbook file."),
      downloadButton("downloadData", label = "Download patient data", class = "btn-download")  
    )
  ),
  
  fluidRow(
    width = 12,
    h3("GP Contact, Diagnosis and Prescription Timeline"),
    hr(),
    p("The time series below visualises patient X's GP contact history, displaying diagnoses, prescriptions, and assay results."),
    plotlyOutput("combined_plot", height = "700px", width = "100%"),  # Wrapped in div for styling
    )
  )



# Server logic
server <- function(input, output) {
  
  ## Reactive expression to filter data by selected patient
  Pt_Wide_reactive <- reactive({
    req(input$patient_names)
    Pt_Proc_Wide %>%
      filter(Patient_Name == input$patient_names) %>%
      mutate(Contact_Event_Date = as.Date(Contact_Event_Date, format = "%Y-%m-%d"))  # Ensure correct date format
})
  
output$combined_plot <- renderPlotly({
  filtered_data <- Pt_Wide_reactive()
  
  if (nrow(filtered_data) == 0) {
    showNotification("No data available for the selected patient.", type = "warning")
    return(NULL)
  }
  
  ## Function to create dynamic Y-axis labels for biomedical tests or drugs
  create_dynamic_label <- function(data, test_col = NULL, unit_col = NULL, drug_col = NULL, drug_unit_col = NULL, is_test = TRUE) {
    if (is_test) {
      first_non_na_test <- data[[test_col]][!is.na(data[[test_col]])][1]
      first_non_na_unit <- data[[unit_col]][!is.na(data[[unit_col]])][1]
      
      if (!is.na(first_non_na_test)) {
        return(paste(first_non_na_test, "<br>", first_non_na_unit))
      }
    } else {
      first_non_na_drug <- data[[drug_col]][!is.na(data[[drug_col]])][1]
      first_non_na_drug_unit <- data[[drug_unit_col]][!is.na(data[[drug_unit_col]])][1]
      
      if (!is.na(first_non_na_drug)) {
        return(paste(first_non_na_drug, "<br>", first_non_na_drug_unit))
      }
    }
    return("Unknown Value")
  }

  # Creating the plots as before
  plot_1 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Biomedical_Value_1", "Biomedical_Test_1", "Biomedical_1_Units", "blue")
  plot_2 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Drug_1_Value", "Drug_Name_1", "Drug_1_Units", "lightblue")
  plot_3 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Biomedical_Value_2", "Biomedical_Test_2", "Biomedical_2_Units", "orange")
  plot_4 <- create_time_series_plot(filtered_data, "Contact_Event_Date", "Drug_2_Value", "Drug_Name_2", "Drug_2_Units", "yellow")

  # Collecting valid plots
  plot_list <- list(plot_1, plot_2, plot_3, plot_4)
  valid_plots <- Filter(Negate(is.null), plot_list)

  if (length(valid_plots) == 0) {
    showNotification("No valid plots available for the selected patient.", type = "warning")
    return(NULL)
  }

  ## Creating dynamic Y-axis labels with line breaks
  y_label_1 <- create_dynamic_label(filtered_data, test_col = "Biomedical_Test_1", unit_col = "Biomedical_1_Units", is_test = TRUE)
  y_label_2 <- create_dynamic_label(filtered_data, drug_col = "Drug_Name_1", drug_unit_col = "Drug_1_Units", is_test = FALSE)
  y_label_3 <- create_dynamic_label(filtered_data, test_col = "Biomedical_Test_2", unit_col = "Biomedical_2_Units", is_test = TRUE)
  y_label_4 <- create_dynamic_label(filtered_data, drug_col = "Drug_Name_2", drug_unit_col = "Drug_2_Units", is_test = FALSE)

  # Create combined subplot only if there are valid plots
  combined_plot <- subplot(valid_plots, 
                           nrows = length(valid_plots), 
                           shareX = TRUE, 
                           titleX = TRUE) %>%
    layout(
      xaxis = list(rangeslider = list(visible = FALSE), fixedrange = TRUE),
      yaxis = list(showticklabels = TRUE, automargin = TRUE),
      yaxis2 = list(showticklabels = TRUE, automargin = TRUE),
      yaxis3 = list(showticklabels = TRUE, automargin = TRUE),
      yaxis4 = list(showticklabels = TRUE, automargin = TRUE),
      
      ## Adding annotations to replace Y-axis titles with horizontal text
      annotations = list(
                         list(x = -0.10, y = 0.90, text = y_label_1, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12)),
                         list(x = -0.10, y = 0.63, text = y_label_2, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12)),
                         list(x = -0.10, y = 0.38, text = y_label_3, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12)),
                         list(x = -0.10, y = 0.12, text = y_label_4, showarrow = FALSE, xref = "paper", yref = "paper", 
                              xanchor = "center", yanchor = "middle", textangle = 0, font = list(size = 12))
                       )
                     )

  combined_plot
})

  ## Generating patient report based on selected patient
  output$patient_report <- renderUI({
  filtered_data <- Pt_Wide_reactive()
  
  if (nrow(filtered_data) == 0) {
    return("No data available for the selected patient.")
  }
  
  patient_name <- trimws(filtered_data$Patient_Name[1])
  patient_gender <- trimws(filtered_data$Patient_Gender[1])
  
  diagnoses <- filtered_data %>%
    select(First_Diagnosis, Second_Diagnosis, Contact_Event_Date) %>%
    filter(!is.na(First_Diagnosis) | !is.na(Second_Diagnosis))
  
  ## Diagnosis logic
  diagnosis_report <- "No formal diagnoses to date."
  if (nrow(diagnoses) > 0) {
    diagnosis_entries <- character()
    
    if (!is.na(diagnoses$First_Diagnosis[1])) {
      first_diagnosis <- trimws(diagnoses$First_Diagnosis[1])
      first_diagnosis_date <- diagnoses$Contact_Event_Date[which(!is.na(diagnoses$First_Diagnosis))[1]]
      diagnosis_entries <- c(diagnosis_entries, paste(first_diagnosis, "on", format(first_diagnosis_date, "%d/%m/%Y")))
    }
    
    if (!is.na(diagnoses$Second_Diagnosis[1])) {
      second_diagnosis <- trimws(diagnoses$Second_Diagnosis[1])
      second_diagnosis_date <- diagnoses$Contact_Event_Date[which(!is.na(diagnoses$Second_Diagnosis))[1]]
      diagnosis_entries <- c(diagnosis_entries, paste(second_diagnosis, "on", format(second_diagnosis_date, "%d/%m/%Y")))
    }
    
    if (length(diagnosis_entries) > 0) {
      diagnosis_report <- paste("Patient diagnosed with", 
                                 paste(diagnosis_entries, collapse = " and "), 
                                 sep = " ")
    }
  }
  
  ## Prescription logic
  prescriptions <- filtered_data %>%
    select(First_Drug_Name, Second_Drug_Name, Contact_Event_Date) %>%
    filter(!is.na(First_Drug_Name) | !is.na(Second_Drug_Name))

  prescription_report <- "No prescriptions to date."
  if (nrow(prescriptions) > 0) {
    prescription_entries <- character()
    
    if (!is.na(prescriptions$First_Drug_Name[1])) {
      first_drug <- trimws(prescriptions$First_Drug_Name[1])
      first_drug_date <- prescriptions$Contact_Event_Date[which(!is.na(prescriptions$First_Drug_Name))[1]]
      prescription_entries <- c(prescription_entries, paste(first_drug, "on", format(first_drug_date, "%d/%m/%Y")))
    }
    
    if (!is.na(prescriptions$Second_Drug_Name[1])) {
      second_drug <- trimws(prescriptions$Second_Drug_Name[1])
      second_drug_date <- prescriptions$Contact_Event_Date[which(!is.na(prescriptions$Second_Drug_Name))[1]]
      prescription_entries <- c(prescription_entries, paste(second_drug, "on", format(second_drug_date, "%d/%m/%Y")))
    }
    
    if (length(prescription_entries) > 0) {
      prescription_report <- paste("Patient prescribed", 
                                   paste(prescription_entries, collapse = " and "), 
                                   sep = " ")
    }
  }
  
  if (!grepl("\\.$", diagnosis_report)) {
    diagnosis_report <- paste0(diagnosis_report, ".")
  }

  if (!grepl("\\.$", prescription_report)) {
    prescription_report <- paste0(prescription_report, ".")
  }

  ## Creating the final report
  report <- HTML(paste("<strong>Patient Name:</strong>", patient_name, "<br>",
                       "<strong>Sex:</strong>", patient_gender, "<br>",
                       "<strong>Diagnosis:</strong>", diagnosis_report, "<br>",
                       "<strong>Prescription(s):</strong>", prescription_report))
  report <- trimws(report)
  return(report)
})
  
  output$downloadData <- downloadHandler(
    filename = function() {
      paste("Theograph_Patient_Summary_", Sys.Date(), ".xlsx", sep = "")
    },
    content = function(file) {
      filtered_data <- Pt_Wide_reactive()
      write.xlsx(filtered_data, file)  
    }
  )
  
}

# Run the app
shinyApp(ui = ui, server = server, options = list(height = 1150))
```